TITLE

### 2023-11-01 archive/L1_P2_TropicalAndes_plant_species_synonyms.Rmd

#Using taxize
```{r}
species_synonyms <- synonyms(GBIF_species_list$Scientific.Name, db = "pow", rows = 1)
```

# Using taxadb
```{r}
#get IDS for each scientific name
syn1<-GBIF_species_list %>%
  mutate(ID=get_ids(Scientific.Name,"itis"))

#Deal with NAs (one name corresponds to more than 1 ITIS code)
syn1_NA<-as.data.frame(syn1$Scientific.Name[is.na(syn1$ID)])
colnames(syn1_NA)<-c("name")

>>>>

#Using taxize
```{r}
species_synonyms <- synonyms(GBIF_species_list$Scientific.Name, db = "pow")
```

# Using taxadb
```{r}
#get IDS for each scientific name
syn1<-GBIF_species_list %>%
    select(Scientific.Name) %>%
    mutate(ID=get_ids(Scientific.Name,"itis"))
```

```{r}
#Deal with NAs (one name corresponds to more than 1 ITIS code)
syn1_NA<-as.data.frame(syn1$Scientific.Name[is.na(syn1$ID)])
colnames(syn1_NA)<-c("name")

### 2023-11-01 code/L0/L0_TropicalAndes_plants_BIEN_occ.Rmd

# Load Tropical Andes moist lowland and montane forest shape
```{r}
TropicalAndes_IUCNHabitat_Forest <- st_read(file.path(data_path, "TropicalAndes_IUCNHabitat_Forest.shp"))
```

# Get occurrence data for Tropical Andes from BIEN database
```{r}
TropicalAndes_BIEN_occ <- BIEN_occurrence_sf(TropicalAndes_IUCNHabitat_Forest, all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)
```

>>>>

# Retrive occurrence data for Tropical Andes countries from BIEN database

## List of desired countries
```{r}
TA_countries <- c("Bolivia", "Ecuador", "Venezuela", "Colombia", "Peru")
```

## Get occurrence data from BIEN
```{r}
TropicalAndes_BIEN_occ <- BIEN_occurrence_sf(TropicalAndes_IUCNHabitat_Forest, all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)
```

### 2023-11-01 code/L0/L0_TropicalAndes_plants_GIFT.Rmd

```{r}
# convert numberic traits into characters so we can combine into one dataframe
height_mean$trait_value <- as.character(height_mean$trait_value)
height_min$trait_value <- as.character(height_min$trait_value)
height_max$trait_value <- as.character(height_max$trait_value)
lifespan$trait_value <- as.character(lifespan$trait_value)
fruit_length_mean$trait_value <- as.character(fruit_length_mean$trait_value)
fruit_length_min$trait_value <- as.character(fruit_length_min$trait_value)
fruit_length_max$trait_value <- as.character(fruit_length_max$trait_value)
seed_mass_mean$trait_value <- as.character(seed_mass_mean$trait_value)
seed_mass_min$trait_value <- as.character(seed_mass_min$trait_value)
seed_mass_max$trait_value <- as.character(seed_mass_max$trait_value)
seed_length_mean$trait_value <- as.character(seed_length_mean$trait_value)
seed_length_min$trait_value <- as.character(seed_length_min$trait_value)
seed_length_max$trait_value <- as.character(seed_length_max$trait_value)
seed_width_mean$trait_value <- as.character(seed_width_mean$trait_value)
seed_width_min$trait_value <- as.character(seed_width_min$trait_value)
seed_width_max$trait_value <- as.character(seed_width_max$trait_value)
```

>>>>

```{r}
# convert numeric traits into characters so we can combine into one dataframe
height_mean$trait_value <- as.character(height_mean$trait_value)
height_min$trait_value <- as.character(height_min$trait_value)
height_max$trait_value <- as.character(height_max$trait_value)
lifespan$trait_value <- as.character(lifespan$trait_value)
fruit_length_mean$trait_value <- as.character(fruit_length_mean$trait_value)
fruit_length_min$trait_value <- as.character(fruit_length_min$trait_value)
fruit_length_max$trait_value <- as.character(fruit_length_max$trait_value)
seed_mass_mean$trait_value <- as.character(seed_mass_mean$trait_value)
seed_mass_min$trait_value <- as.character(seed_mass_min$trait_value)
seed_mass_max$trait_value <- as.character(seed_mass_max$trait_value)
seed_length_mean$trait_value <- as.character(seed_length_mean$trait_value)
seed_length_min$trait_value <- as.character(seed_length_min$trait_value)
seed_length_max$trait_value <- as.character(seed_length_max$trait_value)
seed_width_mean$trait_value <- as.character(seed_width_mean$trait_value)
seed_width_min$trait_value <- as.character(seed_width_min$trait_value)
seed_width_max$trait_value <- as.character(seed_width_max$trait_value)
```

### 2023-11-01 code/L1/L1_P4_TropicalAndes_plant_imputetraits.Rmd

---
title: "TITLE"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script subsets plant occurrence data to species with complete trait coverage."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

>>>>

---
title: "TITLE"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script fill plant trait gaps with imputation."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---
